% \documentclass[11pt,letterpaper]{article}

\documentclass{article}
\usepackage[margin=.5in]{geometry}
\usepackage{anyfontsize}
\usepackage[none]{hyphenat}
\usepackage{enumitem}

\pdfpagewidth 8.5in
\pdfpageheight 11in
\usepackage{xhfill}
\def\Vhrulefill{\leavevmode\leaders\hrule height 1.0ex depth \dimexpr1.0pt-0.7ex\hfill\kern0pt}
\newcommand{\HRule}{\rule{\linewidth}{0.4mm}}

\begin{document}
% \newcommand{\HRule}{\rule{\linewidth}{0.3mm}}



\begin{center}
\textbf{{\LARGE {\Huge {KEVIN WANG}}}} \\ 
{\fontsize{11}{13.2} kwang30@gmail.com  $|$ linkedin.com/in/kwang30 $|$ github.com/kwang30 \\
914 860 4532 $|$ Sunnyvale, CA $|$ Irvington, NY}\\[1ex]
\end{center}
\vspace{-2mm}
\normalsize

\noindent
\textbf{{\Large Education}}\\[-2mm]
\HRule\\
\textbf{Brandeis University} (Waltham, MA)
\hfill Expected May 2018 \\
\indent
BS, Computer Science and Business Administration
\hfill{GPA: 3.3, Deans List}\\
\textit{\textbf{Related Coursework(*Fall 2017)}}: Advanced Programming, Matlab Image Processing, Discrete Math/Intro Proofs, Probability\&Statistics, {\textbf{Data Structures and Algorithms, Database Management Systems, *Operating Systems, *Software Engineering, *Capstone Project, *Android Application Development, *iOS Swift Development (Udemy).}}
\vspace{2mm}


\noindent
\textbf{{\Large Technical Skills}}\\[-2mm]
\HRule\\
\textbf{Programming:} Java, SQL, Ruby/Rails, Matlab, Python, C, HTML/CSS/JavaScript, VBA, \LaTeX, Linux \vspace{2mm}

\noindent
\textbf{{\Large Work Experience}}\\[-2mm]
\HRule\\
\noindent
\textbf{Brown Brothers Harriman Quality Assurance Intern $|$ Boston, MA}
\hfill June 2017 - Aug 2017

\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Collaborated with managers and developers to translate business requirements into test cases and scripts.
\vspace{-2.5mm}
\item Developed SQL queries and test scripts to validate database information on essential tools and applications.
\vspace{-2.5mm}
\item Improved time to deploy new software by performing regression tests and running test scripts on applications.
\end{itemize}
\vspace{-2.0mm}

\noindent
\textbf{Pearson Ham Consulting Data Analyst Intern $|$ London, U.K}
\hfill June 2016 - Aug 2016 

\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Developed VBA Scripts with Google Maps API to translate geospatial data into city names for data analysis.
\vspace{-2.0mm}
\item Synthesized and created new datasets for data analytics and business intelligence reports.
\vspace{-2.5mm}
\item Created and designed an automated dashboard using SQL/VBA to monitor pricing models.
\end{itemize}
\vspace{-2.0mm}

\noindent
\textbf{NY State Assembly Legislative Intern $|$ Tarrytown, NY}
\hfill June 2017 - Aug 2017

\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Conducted research on various topics to assist the Assemblyman in developing local policies and legislation.
\vspace{-2.5mm}
\item Communicated with government officials about proposed legislation and interacted with constituents about their concerns.
\end{itemize}



\noindent
\textbf{{\Large Related Projects}}\\[-2mm]
\HRule\\
\noindent
\textbf{WExchange(Ruby on Rails)}
\hfill Sept 2017 - Present 
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Developing database backed Ruby on Rails web application that connects content creators to buy/request and sell artwork with an integrated calendar and payment system.
\vspace{-2.5mm}
\item Developing rails backend by creating data models for database schema design and integrating payment system with Stripe API. 
\end{itemize}
\vspace{-2.0mm}


\noindent
\textbf{Unix Emulator(Java, Unix)}
\hfill Sept 2017 - Present 
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Developing a Unix-like shell with multi-threaded programming techniques, to achieve concurrent and asynchronous commands and pipeline-like input/output redirections.
\vspace{-2.5mm}
\item Designing a simulation of UNIX File System that provided a standard
seek/read/write interface.
\end{itemize}
\vspace{-2.0mm}


\noindent
\textbf{Twitter Makrov Chain Bot(Python)}
\hfill Sept 2017 - Sept 2017
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Developed Twitter Bot with Reddit and Twitter APIs in python to generate tweets based on Reddit posts using Markov Chains.
\end{itemize}
\vspace{-2.0mm}

\noindent
\textbf{Database Interface and B+ Tree(Java, PostgreSQL, JDBC}
\hfill March 2017 - June 2017 
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Implemented B+ Tree in Java for database indexing, insertion, deletion, search,
redistribution, combination.
\vspace{-2.5mm}
\item Implemented a PostgreSQL database interface using JDBC to support data visualization with Gnuplot, Graphviz and LaTex APIs. Designed integrity constraints and triggers to maintain the database.
\end{itemize}
\vspace{-2.0mm}



\noindent
\textbf{Signal Processing Analytics(Matlab)}
\hfill Feb 2016 - May 2016
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Implemented auditory algorithms to extract tempo, beat, and key of songs using the signal processing toolbox in MATALB by conducting frequency envelope extraction, peak picking, and audio filtering.
\vspace{-2.5mm}
\item Conducted customer analytics of listening patterns using the statistical analysis toolbox of various songs.
\end{itemize}



\noindent
\textbf{{\Large Leadership Experience}}\\[-2mm]
\HRule\\
\noindent
\textbf{Computer Science Club - Member}
\hfill Aug 2014 - Present 
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Help organize and attend various events relating to hackathons, data analytics, and software/web development.
\end{itemize}
\vspace{-2.0mm}

\noindent
\textbf{Southeast Asia Club - Treasurer}
\hfill Apil 2016 - Present
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Update club financial data with university database to track accurate club revenue and expense accounts.
\vspace{-2.5mm}
\item Manage an annual \$15,000+ annual budget, fundraising efforts, and financial negotiations with the club.
\end{itemize}
\vspace{-2.0mm}

\noindent
\textbf{Jaded Literary Magazine - Treasurer, President}
\hfill Aug 2015 - Present
\begin{itemize}[leftmargin=*]
\vspace{-2.5mm}
\item Organize a \$6,000+ annual budget to magazine publication and events held every semester.
\vspace{-2.5mm}
\item Manage the rollout of magazine publications, finalizing content, an designing layout every semester. 
\vspace{-2.5mm}
\end{itemize}
\vspace{-2.0mm}

\pagenumbering{gobble}

% \pagenumbering{gobble}
%\end{resume}
\end{document}